\documentclass{article}[twocolumn]
\usepackage{graphicx}
\usepackage[includeheadfoot, top=0.5in, bottom=0.5in, hmargin=0.5in]{geometry}
\usepackage{multicol}
\date{\today}

\newcommand{\bb}[1]{\item[] \textbf{#1}}

\begin{document}
\begin{multicols}{2}
\section{Source 1: Elle
}
\begin{enumerate}
     \bb{Sagittarius}
    \item Stay strong, X. The focalizing Sun in your mindset court is at odds with chaotic Uranus in your salubrious sixth house today, making it more difficult for you to stay firmly onboard the wellness wagon. Maybe you have every intention of staying the course, but a stressful day at work, circumstances that seem to change on a dime, or low energy is causing you to reach for comfort food and caffeine. But you won’t feel your best if you go that route, and deep down, you know it. Healthy habits will get you through these hectic times, so grab an apple, a handful of walnuts and a soothing cup of herbal tea instead.\\
     \bb{Aquarius}\
    \item You’re just not in the mood for making selfless sacrifices today, and that’s okay, X. With the self-focused Sun in your sign battling your ruler, renegade Uranus, in your cozy fourth house, you’re due for some downtime so you can replenish your reserves. Don’t flake on your family, housemates or loved ones. Just let them know you need to chill solo for a while. Even if they whine a little, they’ll find someone else to fulfill their request. Self-care needs to be your top priority now.
     \bb{Leo}
    \item Your professional responsibilities and personal life could clash today as your ruler, the radiant Sun, in your relationship realm locks horns with wrench-throwing Uranus in your career corner. You might need to bow out of an engagement tonight so you can deal with a crisis on the job. But first, ask yourself whether someone might be shirking their duties and pushing them onto your plate instead. Just because you CAN handle this assignment doesn’t mean you should, generous X. If your dinner date matters just as much to you as earning brownie points at the office, consider clocking out on time.
     \bb{Cancer}
    \item Someone could test your loyalty today, X. Although your sensitive, caring sign is likely to pass, with curveball-throwing Uranus in the mix, it wouldn’t hurt for you to consider this pro tip: Give your current commitments top priority rather than allowing yourself to get distracted by an interesting option. It might not seem like a big deal to ask for a raincheck, but play it safe and stick to the plan. You of all people don’t want to risk hurting a friend’s feelings.
     \bb{Gemini}
    \item You can’t afford to be naïve today, X. Under a tense square between the egoistic Sun and unpredictable Uranus, someone could try to pull the wool over your eyes. If you start doubting the worth of your work, even though you know you’ve performed well, that might be a sign that a savvy manipulator is messing with your head. Maybe you do still have more to prove, and playing right into this person’s hands will set you up for failure. If an assignment is way outside your wheelhouse, your best bet might be to turn it down so you don’t have to fake your way through it.
     \bb{Virgo}
    \item You may have a hard time maintaining your concentration under today’s distracting square between the Sun and erratic Uranus. One side of you is fired up to put your nose to the grindstone and get ‘er done. But another side has a wild hair to take off on a tangent and enjoy your freedom. Think long and hard about tackling a complex project that requires your full attention. You’re better off toggling between a couple of assignments and taking mini-breaks to roam and recharge.
     \bb{Libra}
    \item Being a “people person” doesn’t make you a mind-reader, X. Under today’s tense square between the egoistic Sun and enlightening Uranus, everyone seems to assume you can guess their meaning, even if it’s as clear as mud. Trying to translate their scrambled signals accurately will only confuse things further. Instead of wasting time attempting to crack the code, call people out on their obfuscating behavior. But don’t jump to the conclusion that they’re confusing you intentionally. They may not even know how bewildering they’re being!
     \bb{Taurus}
    \item As one of the zodiac’s most reliable signs, you might find the role of “the grownup in the room” to be a natural fit. But with the self-focused Sun battling renegade Uranus in X today, you’re likely to chafe at that responsibility. Still, if you’ve already offered to take on certain duties, you could hurt your reputation if you bow out now. Try divvying up tasks to leave more space in your calendar for unstructured play. And if someone is slacking off, give a stronger recruit the nod.
     \bb{Scorpio}
    \item Even if you’re feeling good about a budding friendship, it’s not your style to rush things and overshare. Maybe this person is pushing the pace and encouraging you to bare your soul, but today’s tense square between the self-focused Sun in your sensitive fourth house and unpredictable Uranus in your interpersonal zone warns against TMI. Don’t feel obligated to listen supportively if they’re confiding in you like a BFF. Send a clear signal that you need to slow things down. That way, you’ll buy some time to decide whether you’re ready to see the skeletons in their closet.
     \bb{Capricorn}
    \item During today’s dustup between the Sun and erratic Uranus, love and money don’t mix. You could try to have a calm conversation about finances with your bae, and then talks quickly turn tense. Rather than staging a dramatic confrontation, first do some fiscal organizing on your own so you can initiate a dialogue (maybe tonight or tomorrow) with a well-thought-out plan and useful ideas. Single X shouldn’t assess romantic prospects based on their net worth. That said, be on guard for anyone who’s hoping to ride YOUR coattails.
     \bb{Pisces}
    \item Don’t do anything rash today when the egoistic Sun in your subconscious sector squares off with disruptive Uranus in your communication center. You might suddenly feel like you can’t hang around for one more second, and you urgently need to find the nearest exit. But you can claim personal space for yourself without picking a fight or breaking up with someone. Slip out of a gathering or politely excuse yourself and head home for a mellow night at the X Palace. You’ll have a different perspective tomorrow.
     \bb{Aries}
    \item Don’t be too quick to reach for the bill and declare, “Lunch is on me.” Draw a clear line today when groups and money become a tricky mix under a Sun-Uranus showdown. If a work team or friend group assumes you’re cool with contributing more than your fair share because you haven’t spoken up in the past, it’s time to set limits. Is your squad’s expensive taste blowing your budget? Suggest a more affordable restaurant and be honest about your budget. You don’t need to save face. You need to save money!
\end{enumerate}

\section{Source 2: Washington Post
}
\begin{enumerate}
     \bb{Sagittarius}
    \item You have some crazy friends, but one in particular stands head and shoulders above the rest. Should you dismiss them entirely, help this person find some psychological counseling or just pretend it never happened? Weigh the seriousness of the situation before you do anything at all. Sometimes it's best just to coast and let the Universe work it out.
     \bb{Aries}
    \item You're still feeling solid, practical, responsible, and grounded. Good. Considering what might tumble out of your mouth today, you're going to need a healthy dose of confidence. What's it going to be? It's tough to say, but it won't be something you or anyone around you could ever have predicted. Almost sounds like fun, doesn't it?
     \bb{Leo}
    \item Everyone's going to be quite chatty today, no doubt about it. But you? You're going to be even more verbally reckless than usual. It's not like you've ever needed any help getting inspired to say exactly what you want to say, and the heck with the consequences, so just imagine what today's verbosity will bring. You'd better warn anyone who startles easily. Or not.\\
     \bb{Libra}
    \item You've been waiting for the right moment to let someone know you're not a child any more. You're perfectly capable of making your own choices and you don't need their advice. And you had just about decided to make the announcement when you realized they actually had something quite valuable to share. Better hold off on the declaration of independence for a bit.\\
     \bb{Gemini}
    \item At this point, your friends are pretty well trained. Most of them don't even bat an eye when you get going on one of your favorite subjects, even if it's in a public place. They've learned that resistance is futile, and besides, you're usually quite entertaining to watch. Today, however, even the most seasoned among them will be hard-pressed to keep a straight face. Of course, you may have an equally hard time too. One never knows what you might say or do. \\
     \bb{Capricorn}
    \item They'll sit down across from you, or stand right there in front of you, cross their arms, and look you straight in the eye. Then they'll ask if you'd please share your opinion of the current situation with them, one-on-one, as a favor and in confidence. Try not to be rude. You were already getting ready to let the world know your take, but it wouldn't hurt to let them think they were responsible for the big revelation. \\
     \bb{Taurus}
    \item It's just your nature to wonder. But when you do too much of it, it can easily turn into an obsession. Keeping that in mind, could it be time to stop worrying if a deeper meaning was behind that comment a loved one recently made. You're a natural-born detective, but some clues just aren't worth following. And some folks aren't clever enough to insert actual meaning into everything they say.
     \bb{Scorpio}
    \item You're done talking about the issue that's been making you crazy for weeks, if not months. You're so done that even when a certain someone who's ordinarily quite good at pushing your buttons starts to subtly poke at you, you won't bite. It wouldn't be fair, and it wouldn't even be fun. You know you can win, and win easily, but you can't justify the energy. It's just as well. You have bigger fish to fry. \\
     \bb{Pisces}
    \item You've never been fond of blind dates. But now, after one too many interesting experiences, to say you're less than fond of them wouldn't quite cover your sentiments. For some darned reason, though, a friend or family member is insisting there's someone you "just have to meet." Who knows? They could be right this time. Just don't sign up for dinner. Suggest coffee or drinks, and duck out early if you need to. \\
     \bb{Virgo}
    \item Telling you not to go out and spend your every dime on a lark, with absolutely no thought for the future, just isn't going to work. Asking you not to won't work either. What if someone who loves you reminds you of the bills that will be turning up right around the same time your mortgage payment's due? That might work, but there are still no guarantees. This time you just may need to muster up the willpower yourself.\\
     \bb{Cancer}
    \item From the very moment you got up this morning, you've been in a rather odd mood. You don't want to do anything the way you used to do it, and you don't particularly care if that offends anyone. You're not even trying to compromise. Since this is an unusual attitude for you, don't be surprised if your loved ones are a bit stunned. They're sure to get a big kick out of it, though! \\
     \bb{Aquarius}\
    \item Your spiritual and psychic qualities are running on high right now. So if you suddenly get the feeling you don't want to be where you are, or that you'd like someone else to be there with you, don't even bother resisting. Do what it takes to make yourself comfortable and happy. You've connected with the powers that be, and they're directing you. Sure, it sounds corny, but just go with it.\\
\end{enumerate}
\section{Source 3: Horoscope.com
}

\begin{enumerate}
 \bb{Scorpio}
\item Your internal computer just got upgraded today and your head is buzzing with all kinds of new information, X. The good news is that you should be able to process all these bytes at lightning speed. Act swiftly and with great confidence. You can do anything. You could even talk your way into the White House for dinner.\\ 
 \bb{Virgo}
\item If you don't understand something, ask, X. If it looks different to you, ask why that is. Your curiosity is high, especially when it comes to the unconventional, and even more if it's revolutionary. The rebel in you will feel new purpose, and you may be tempted to throw a stick in the spokes of an old carriage that continues to head down the same old boring path.\\ 
 \bb{Libra}
\item You may be shaken to the core today by someone of great personal magnetism, X. Maybe you feel as if you're being overshadowed because of the grandiose ideas and mountains of information coming from this person. Perhaps you feel you're too slow. Did you ever think that someone is going too quickly? Don't automatically think that you're the one who needs to change gears.\\ 
 \bb{Aquarius}
\item Aggressive people may interfere with your plans today, X, so don't get too upset if things don't work out the way you want them to. Let this be an exercise in learning how to think and act on your feet. Remember that you can play this game as well as others. Deliver an unexpected surprise right back and see how they deal with it. Perhaps you can learn something.\\ 
 \bb{Sagittarius}
\item You may feel a bit lonely today, X, even if there are people all around you. It may seem like everyone's on a different plane. Maybe you think you have nothing in common with others - even those you generally feel closest to. You may be apprehensive about what they think of you after you tell them what you're really thinking or feeling. Don't let this stop you from making your thoughts known.\\ 
 \bb{Gemini}
\item Today you may be asked to choose between the old and the new, X. It's as if people are protesting in some manner and you're being asked to join in the ranks of those wishing to see change. Make sure you honestly assess all the available information before you automatically dismiss the situation as foolish. You should seriously consider lending a hand to the fight. \\ 
 \bb{Aries}
\item Like a team of pickpockets in a crowd, a group may have its eyes on you and secretly scheme to take advantage of your innocence, X. One may work to distract you with something playful and harmless, while the others work behind your back to secretly steal your valuables. Stay aware of yourself and your belongings at all times.\\ 
 \bb{Cancer}
\item Your inner strength and courage are tremendous today. You will find that people naturally gravitate toward you, X. Accept this flood of energy and put it to good use however you see fit. A spark of genius may hit you sometime during the day. It will have you up all night working on a new invention.\\ 
 \bb{Leo}
\item Wear the striped shirt and polka-dot pants today, X. The more you clash with the outside world the better. You may feel wildly out of place at first, but you will begin to see the beauty, importance, and respect you hold by standing out from the crowd. This attitude change will do you good. You may see a whole new way of living.\\ 
 \bb{Pisces}
\item It's hard to keep your balance when a big rock suddenly falls on one side of the scale, X. Resolving the matter isn't as hard as you think, because this rock has been dropped there as a gift. Even though it might be shocking at first, there's an important message in this surprise. The tricky part is figuring out what it is.\\ 
 \bb{Taurus}
\item Opportunity is the name of the game for you, X. Don't turn out the lights before you make sure you've explored all your options today. Inspiration may come in a flash of unexpected thought, so make sure you have a pad and pencil handy. A good idea could be disguised as something insignificant, but if anyone is able to see the potential in something, it's you.\\ 
 \bb{Capricorn}
\item This is a climactic time for you, X. All your yearly cycles have reached a critical juncture. You may feel as if you're at a point of tremendous victory or terrible failure. Either way, it's important that you look on this time as a celebration that you've made it this far. Make changes where necessary and continue to reevaluate your progress over the next few months.\\ 
\end{enumerate}

\end{multicols}
\end{document}
